% Display all inline math symbols like in math mode.
\everymath{\displaystyle}

% "leqno" = "Left equation numbering"
\documentclass[leqno,12pt]{article}

% Tree drawing.
\usepackage{tikz}

% More control over enumerations.
\usepackage{enumitem}

% Font color options.
\usepackage{xcolor}

% Clickable cross-references for enumerations and so on.
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

% Needed for umlauts etc. to be read correctly from the source file.
\usepackage[utf8]{inputenc}

% Font encoding of the PDF.
\usepackage[T1]{fontenc}

% German hyphenation patterns, date format, strings and so on.
%\usepackage[ngerman]{babel}

% English document.
\usepackage[english]{babel}

% Load font here.

% Latin Modern font instead of the default Computer Modern font.
\usepackage{lmodern}

% Improve text rendering.
\usepackage{microtype}

% Set page margin.
\usepackage[a4paper]{geometry}

% Box drawing for multi-line equations.
% Implicitly imports mathtools and amsmath.
\usepackage{empheq}

% q.e.d. symbol and so on.
\usepackage{amsthm}

% Extended set of symbols (implicitly imports amsfonts).
\usepackage{amssymb}

% More symbols like "\lightning".
\usepackage{wasysym}

% Define "\biggg" and "\bigggg" for even bigger symbols.
% Define "\sothat" for set relation symbol and correct spacing.
\makeatletter
\newcommand\biggg{\bBigg@{2.5}}
\newcommand\bigggg{\bBigg@{3}}
\newcommand\sothat{\, \middle\vert \,}
\makeatother

% Define underscore character as "\_".
\chardef\_=`_

% Remove section and subsection counters while keeping the table of contents.
\setcounter{secnumdepth}{0}

\title{Mason \\ Programming Language Specification}
\author{Mike Jasinski}
%\date{}

\begin{document}
    \maketitle
    \thispagestyle{empty}
    \newpage
    \tableofcontents
    \newpage

    \section{Introduction}
    Mason is a system programming language that values simplicity, maintainability,
    productivity and performance. It is designed and built for modern computers,
    and aims to increase developer productivity by decreasing the friction between the programmer
    and the programming language. It features strong, static typing, complete control
    over data structures and memory allocation strategies, and a fast and lean standard
    library.

    \section{Notation}
    The syntax of a feature is described when the feature is described. Additionally,
    it can be inferred from code examples at various points in this document.
    A BNF definition may be added at a later point.

    \section{Lexical Elements}
    \subsection{Source Code Representation}
    Source code is text encoded in UTF-8. While Mason makes no effort to support Unicode
    characters for the source itself, they can be used in \hyperref[comments_section]{comments}
    and \hyperref[strings_section]{string} literals.

    \subsection{Tokens}
    Source code is split into tokens during lexical analysis. Whitespace and newline characters
    are ignored and serve as token separators (except in \hyperref[strings_section]{string} literals).
    \bigskip \\
    There are 3 types of tokens:
    \begin{enumerate}
        \item
        \textbf{Identifiers:} Tokens starting with \texttt{\_} or an alphabetical character
        and further characters being \texttt{\_} or alphanumeric. For example:
        \texttt{\_test}, \texttt{var2}, \texttt{obj\_type}.

        \item
        \textbf{Symbols:} \texttt{.} \texttt{,} \texttt{:} \texttt{;} \texttt{"} \texttt{->}
        \texttt{+} \texttt{-} \texttt{*} \texttt{/} \texttt{\textasciicircum} \texttt{\&} and so on.
        They can consist of multiple characters, such as \texttt{->}.

        \item
        \textbf{Literals:}
        \begin{enumerate}
            \item
            \textbf{Integer Literals:}
            \begin{enumerate}[label=(\roman*)]
                \item
                \textbf{Decimal Literals:} Optionally one of $\{\texttt{+}, \texttt{-}\}$ followed by
                a combination of digits $[0,9]$. If the literal has more than one digit,
                there must not be any leading digits equal to $0$. For example, $00012085$ is not
                a decimal literal, but $0$, $22$, and $910492$ are.

                \item
                \textbf{Binary Literals:}
                Not a very important feature, may be added at a later point.
                \item
                \textbf{Hexadecimal Literals:}
                Not a very important feature, may be added at a later point.
            \end{enumerate}

            \item
            \textbf{Floating-Point Literals:}
            \begin{enumerate}[label=(\roman*)]
                \item
                Decimal literal followed by a \texttt{.} and a combination of digits $[0,9]$.
                For example: $3.14159$, $509.12$, $0.0$.
            \end{enumerate}

            \item
            \textbf{String Literals:}
            \begin{enumerate}[label=(\roman*)]
                \item
                UTF-8 text enclosed by \texttt{""}. For example: "Hello World!".
            \end{enumerate}

        \end{enumerate}
    \end{enumerate}

    \subsection{Comments}
    \label{comments_section}
    The token \texttt{//} and any text that follows until end of line is ignored.\\
    The tokens \texttt{/*}, \texttt{*/} and any text in between is ignored.

    \subsection{Strings}
    \label{strings_section}
    ...

    \section{Variables}

    \section{Types}

    \section{Standard Library}
    \subsection{Allocators}

    \section{Context System}
    \subsection{Thread Safety}

    \section{Scopes}

    \section{Modules}

\end{document}